Methods for Large Scale Learning to Rank

### 2014-04-22 report/Chapters/LTRMethods.tex
TODO list voor omschrijven SmoothRank
softmax activatie functie gefixt

\section{SmoothRank}
SmoothRank \cite{Chapelle2010} is a listwise ranking method that directly optimises an information retrieval evaluation measure by smoothing, that is, approximating the rank position. In this section I will use \ac{nDCG} for illustration of SmoothRank, but the same procedure can also be applied to \ac{MAP} or any other information retrieval measure.\\

>>>>

\section{SmoothRank}
SmoothRank \cite{Chapelle2010} is a listwise ranking method that directly optimises an information retrieval evaluation measure by smoothing, that is, approximating the rank position. In this section I will use \ac{nDCG} for illustration of SmoothRank, but the same procedure can also be applied to \ac{MAP} or any other information retrieval measure. The smoothing function used in SmoothRank based on the softmax activation function \cite{Bridle1990} that is often used in neural networks, which is formally defined as shown in \ref{eq:softmax_algorithm}.
\begin{equation}
p_i = \frac{e^{f_i/\sigma}}{\sum\nolimits_{j=1}^{m}e^{f_j/\sigma}}
\label{eq:softmax_algorithm}
\end{equation}

% TODO: 1) Smoothing framework uitleggen en toepassen op nDCG 2) sigma trade-off behandelen 3)Nonlinear conjugate gradient descent uitleggen 4) startin point en regularization uitleggen 5) Annealing process uitleggen %
